### 2017-08-18 paper/incomeShocks-jde-r1.tex
Add descriptive stats tables for women not in main sample

% Attrition descriptive statistics

\begin{table}[htbp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Descriptive statistics for Crop loss and Outcomes}
\label{tab:attrition_desc_stat_croploss}
\begin{tabular}{l  D{.}{.}{2,3} D{.}{.}{2,3} D{.}{.}{2,3} D{.}{.}{2,3} D{.}{.}{2,3}} \toprule
                                  & \multicolumn{4}{c}{Wave} & \mco{Average} \\ \cmidrule(lr){2-5}
                                  &\multicolumn{1}{c}{1} &\multicolumn{1}{c}{2}   &\multicolumn{1}{c}{3} &\multicolumn{1}{c}{4} &   \\ \midrule
Dummy crop loss (1-7 months) $\geq$ TZS 200            &        0.58&        0.22&        0.01&        0.00&        0.34\\
                                                       &      (0.49)&      (0.42)&      (0.12)&      (0.00)&      (0.48)\\ 
\addlinespace 
Currently pregnant                                     &        0.14&        0.10&        0.08&        0.00&        0.11\\
                                                       &      (0.34)&      (0.30)&      (0.27)&      (0.00)&      (0.31)\\
Gave birth since last survey                           &        0.19&        0.12&        0.12&        0.07&        0.15\\
                                                       &      (0.39)&      (0.33)&      (0.33)&      (0.27)&      (0.36)\\
\addlinespace 
Contraceptive use                                      &        0.12&        0.17&        0.15&        0.19&        0.14\\
                                                       &      (0.33)&      (0.37)&      (0.36)&      (0.40)&      (0.35)\\
Contraceptive use -- Traditional\tnote{a}              &        0.08&        0.10&        0.05&        0.11&        0.08\\
                                                       &      (0.27)&      (0.30)&      (0.23)&      (0.32)&      (0.28)\\
Contraceptive use -- Modern\tnote{b}                   &        0.05&        0.07&        0.09&        0.07&        0.06\\
                                                       &      (0.21)&      (0.26)&      (0.29)&      (0.27)&      (0.25)\\ 
\bottomrule
\end{tabular}
\begin{tablenotes} 
\scriptsize
\item[a] Traditional contraceptives include abstinence and rhythm method.
\item[b] Modern contraceptives include condom, diaphragm, pill, IUD, injection, female and 
male sterilization.
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[htbp]
\centering
\footnotesize
\begin{threeparttable}
\caption{Wave 1 Descriptive Statistics for Women}
\label{tab:attrition_desc_stat_women}
\begin{tabular}{l  D{.}{.}{3,2} D{.}{.}{3,2} D{.}{.}{3,2} D{.}{.}{3,2}} \toprule
                            	 & \mco{Mean} 	 & 	\mco{St Dev}	  \\ \midrule
Age 18-22                                              &        0.29&        0.45\\
Age 23-27                                              &        0.17&        0.38\\
Age 28-32                                              &        0.18&        0.38\\
Age 33-37                                              &        0.14&        0.35\\
Age 38-45                                              &        0.22&        0.41\\ 
\addlinespace 
No education                                           &        0.23&        0.42\\
1 - 6 years of education                               &        0.24&        0.43\\
7 plus years of education                              &        0.53&        0.50\\ 
\addlinespace 
Assets per capita in wave 1 (10,000 TZS)\tnote{a}      &        9.24&       21.44\\
\addlinespace 
Number of women                                        &     \mct{207}           \\
\bottomrule
\end{tabular}
\begin{tablenotes} 
\scriptsize
\item[a] Assets capture self-reported values of land, livestock, business assets, durable
goods, and savings.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

% Attrition descriptive statistics across waves
\input{../tables/appendix_desstat2.tex}

\input{../tables/appendix_desstat1.tex}
